### 2017-04-06 paper/evaluation.tex
second par rq5

To answer this research question we surveyed developers involved in a
selection of projects from our benchmark with time-consuming test
suites.  The goal of the survey is to better comprehend developer's
attitude towards the use of parallelism as a mechanism to speedup
regression testing.  We surveyed developers from a total of
\Fix{x=83-11-y} projects.  From the initial list of \numMedLong{}
project, we discarded 11 projects that we knew a priori used
parallelization, and \Fix{y} projects that we could not find
developer's emails from commit logs.  From this list of projects, we
mined potential participants for our study.  More precisely, we
searched for developer's name and email from the last 20 commits to
the corresponding project repository.  Using this approach, we
identified a total of \emailsSent{} eligible participants.  Finally,
we sent plain-text e-mails to those developers with the survey.  In
total, \emailsAnswered{} developers replied but we discarded
\emailsFalseAnswers{} replies with subjective answers.  Considering
projects covered by the answers, a total of \emailsProjectsAnswered{}
projects (\percEmailsProjectsAnswered{} of the total) were represented
in those replies.  Note that multiple developers on each project
received emails.

\Mar{----- estou aqui}

The survey sent was composed by three open questions and one closed
question: (I) How long does it take for test to run in your
environment? Can you briefly define your setup? (II) Do you confirm
that your project does not run in parallel? (III) Select a reason for
not using parallelization: (a) I did not know it was possible; (b) I
was concerned with concurrency issues; (c) I use a continuous
integration server; (d) Some other reason. Please elaborate.

>>>>

To answer this research question we surveyed developers involved in a
selection of projects from our benchmark with time-consuming test
suites.  The goal of the survey is to better comprehend developer's
attitude towards the use of parallelism as a mechanism to speedup
regression testing.  We surveyed developers from a total of
\Fix{x=83-11-y} projects.  From the initial list of \numMedLong{}
project, we discarded 11 projects that we knew a priori used
parallelization, and \Fix{y} projects that we could not find
developer's emails from commit logs.  From this list of projects, we
mined potential participants for our study.  More precisely, we
searched for developer's name and email from the last 20 commits to
the corresponding project repository.  Using this approach, we
identified a total of \emailsSent{} eligible participants.  Finally,
we sent plain-text e-mails to those developers with the survey.  In
total, \emailsAnswered{} developers replied but we discarded
\emailsFalseAnswers{} replies with subjective answers.  Considering
projects covered by the answers, a total of \emailsProjectsAnswered{}
projects (\percEmailsProjectsAnswered{} of the total) were represented
in those replies.  Note that multiple developers on each project
received emails.  We sent the following set of questions to
developers:

\begin{enumerate}
\item How long does it take for test to run in your environment? Can
  you briefly define your setup?
\item Do you confirm that your project does not run in parallel?
\item\label{questionThree} Select a reason for not using parallelization:
  \begin{enumerate}[label=\alph*)]
  \item I did not know it was possible
  \item I was concerned with concurrency issues
  \item I use a continuous integration server
  \item Some other reason. Please elaborate.
  \end{enumerate}
\end{enumerate}
